
---
title: "SPACE"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(ggplot2)
library(dplyr)
library(plotly)
library(shiny)
library(ggplot2)
library(reshape2)
```

# Introduction
This Section will show you how many missions happened in the past and how much success we had in them </br>
Also you will be provided with the country wise contribution and their success and failures yearwise 

# Past Missions

## Column {data-height=1000, .tabset .tabset-fade}

### Overview of yearwise Missions (Interactive) 


```{r}
x=read.csv(file="C:/Users/Anirudh/OneDrive/Desktop/Space_Corrected.csv",header=TRUE)
dates=c(x$Datum)
year=c()
unique_year=c()
for(i in 1:length(dates)){
  year[i]=strtoi(substring(dates[i], 13,16))
}
unique_year=unique(year)
#extracting the years as strings 


place=c(x$Location)
for(i in 1:length(place)){
  temp=c(unlist(strsplit(place[i],",")))
  place[i]=temp[length(temp)]
}
#extracting the countries out of the actual addresses given

success=0
failure=0
temp_year=c(0,0)
temp_success=c(0,0)
temp_failure=c(0,0)
status=c(x$Status.Mission)
data=data.frame(year,place,status)
unique_country=unique(place)
total=data.frame(table(place))
unique_year=unique(year)
freq=c(rep(0,times=length(unique_country)))
for(j in 1:length(unique_country)){
  for(i in 1:length(place)){
    if(tolower(unique_country[j])==tolower(place[i])){
      freq[j]=freq[j]+1
    }
  }
}

`%+=%` = function(e1,e2) eval.parent(substitute(e1 <- e1 + e2))
freq_year=c(rep(0,times=length(unique_year)))
for(j in 1:length(unique_year)){
  for(i in 1:length(year)){
    if(unique_year[j]==year[i]){
      freq_year[j]=freq_year[j]+1
    }
  }
}

custom_df=data.frame(year,x$Status.Mission)
plot=custom_df %>% group_by(year,x.Status.Mission) %>% summarize(n=n()) %>% mutate(pct=n/sum(n),lbl=scales::percent(pct))
plot=cbind(plot,freq_year=c(rep(0,times=nrow(plot))))
year_df=data.frame(unique_year,freq_year)
for(j in 1:nrow(year_df)){
  for(i in 1:nrow(plot)){
    if(plot$year[i]==year_df$unique_year[j]){
      plot$freq_year[i]=year_df$freq_year[j]
    }
  }
}


bp=ggplot(plot,aes( text = paste('</br>Year: ',year,'</br>Status: ',x.Status.Mission,'</br>Total Missions: ', freq_year,'</br>Percentage: ', pct*100,'%')))+geom_bar(aes(year,pct,fill=factor(x.Status.Mission)),stat="identity",position="fill",width=0.9)+scale_y_continuous(seq(0,1,by=0.25),expand = c(0, 0),labels = scales::percent)+scale_fill_manual(values = c("grey0","grey15","grey25","steelblue2"))
bp=bp+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),axis.text=element_text(size=6))
bp=bp+labs(x="Year",y="Percentage",title="Success Vs Failure percentage per year",fill="Mission Status")
ggplotly(bp, tooltip="text")

```

### Overview of yearwise Missions
```{r}
success=0
failure=0
a=1
for(k in 1:length(unique_year)){
  success=0
  failure=0
  
  for(i in 1:length(place)){
    if(year[i]==unique_year[k]){
      if(status[i]=="Success"){
        success%+=%1
      }
      else{
        failure%+=%1
      }
    }
  }
  temp_year[a]=unique_year[k]
  temp_success[a]=(success/(success+failure))*100
  temp_failure[a]=(failure/(success+failure))*100
  a=a+1
}
par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
bp=barplot(t(matrix(c(temp_success,temp_failure),ncol=2)),names.arg=temp_year,xlab="Year",ylab="Percentage",las=3,cex.names=0.6,col = c("steelblue2","black"),main="Success Vs Failure percentage per year",ylim=c(0,100))
legend("topright", inset=c(-0.3,0), legend=c("% success","% failure"),pch=19,col=c("steelblue2","black"))
lines(x=bp,c(freq_year)/2,col="white",lwd=2)

```



## Column {data-width=500}



```{r}
total=total[order(total$Freq,decreasing = TRUE),] #to sort the countries by the total number of missions overall
master_data=list()
heading=c()
temp=0
temp_data=data.frame()
unique_country=total$place
freq=c(total$Freq)
for(j in 1:length(unique_country)){
  a=1
  if(freq[j]>=50){
  for(k in 1:length(unique_year)){
    
    success=0
    failure=0
    
    for(i in 1:length(place)){
      if(tolower(unique_country[j])==tolower(place[i])){
      
        
      
        if(unique_year[k]==year[i]){
          
         
         #one year of one country
          if(tolower(status[i])=="success"){
            #print(status[i])
            success%+=%1
            #print(success)
            
          }
          else{
            #print("aa")
            failure%+=%1
          }
        }
        #inside a country per year success or failure
       
         
      }
    }
    temp_year[a]=unique_year[k]
    temp_success[a]=success
    temp_failure[a]=failure
    a=a+1
    
  }
  #print(unique_country[j])
  #print(data.frame(temp_year,temp_success,temp_failure))
  temp=temp+1
  temp_data=data.frame(temp_year,temp_success,temp_failure)
  heading[temp]=j
  master_data[[temp]]=temp_data
 

  
  }
}


```


```{r}
  selectInput("drop", "Choose plot:", list(1,2,3,4,5,6,7))
```

### Country Plots

```{r}
renderPlot({
data <- master_data[[as.integer(input$drop)]]
data1 <- melt(data[,c('temp_year','temp_failure','temp_success')], id.vars = 1)
ggplot(data1, aes(x=temp_year, y=value, fill=variable),na.rm=TRUE)+geom_bar(stat="identity") + geom_hline(data=data, linetype='dotted', aes(yintercept=mean(temp_success))) + scale_y_continuous(limits = c(0,100)) + xlab("Year") + ylab("Number of missions") + ggtitle(unique_country[heading[as.integer(input$drop)]]) + coord_flip() + scale_fill_manual(values = c("black","steelblue2"), name="Mission Status",labels = c("Failure", "Success"))
})
```


### Pie Charts


```{r}
renderPlot({
data <- master_data[[as.integer(input$drop)]]
data <- group_by(data,temp_year) %>% summarize(count1 = sum(temp_success), count2 = sum(temp_failure))
data1 <- melt(data[,c('temp_year','count2','count1')], id.vars=1)
ggplot(data1, aes(x="", y=value, fill=variable),na.rm=TRUE)+geom_bar(stat="identity") + xlab("Year") + ylab("Number of missions") + ggtitle(unique_country[heading[as.integer(input$drop)]]) + coord_polar("y", start=0, direction=-1) + scale_fill_manual(values = c("black","steelblue2"), name="Mission Status",labels = c("Failure", "Success")) + geom_text(aes(y = sum(value), label=sum(value)), color = "white")

})
```
